\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-22 paper.tex
added three more citations wrt DSL for IDS
improved old evaluation text a bit

For the evaluation we constructed a small meshed network consisting of three
devices, with only one device able to talk to both other devices, requiring
routing of messages through this device.

We started from a basic application that measures light intensity. The
application was written both manually and generated. On top of this baseline we
added two intrusion detection related algorithms: a heartbeat, that allows
nodes to validate each other's continuous presence, and a reputation-building
algorithm that checks if a parent node is cooperative and actually forwards
messages with a destination further down the
network\cite{ganeriwal2008reputation}.

@@

DSL for IDS \cite{eckmann2002statl}

>>>>

For the evaluation we constructed a small meshed network. In this network, not
all devices have direct access to one another, requiring routing through shared
neighboring devices.

We started from a basic application that measures light intensity. The
application was constructed as an includable piece of code. This way it could
be integrated in an manual implementation and merged into the generated
solution. On top of this baseline we added two intrusion detection related
algorithms: a watchdog\cite{mishra2004intrusion}, that allows nodes to validate
each other's continuous presence, and a reputation-building
algorithm\cite{ganeriwal2008reputation}, that checks if a parent node is
cooperative and actually forwards messages with a destination further down the
network.

\subsection{Evaluation}

@@

DSL for IDS \cite{sekar1999high} \cite{uppuluri2001experiences} \cite{eckmann2002statl} \cite{vigna2003designing}
